---
title: "Code Along 6"
subtitle: "High cardinality predictors for #TidyTuesday museums in the UK"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

Our modeling goal is to predict whether a water source actually has water available at it, based on characteristics of the water source observed during a visit. Let’s start by reading in the data.


# Explore Data

```{r}
library(tidyverse)
museums <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-11-22/museums.csv')

```

```{r}
museums %>% count(Accreditation)

museums %>% count(Subject_Matter, sort = TRUE)

top_subjects <- museums %>%
    count(Subject_Matter, sort = TRUE) %>%
    slice_max(n, n = 6) %>%
    pull(Subject_Matter)

top_subjects

museums %>%
    filter(Subject_Matter %in% top_subjects) %>%
    count(Accreditation, Subject_Matter) %>%
    
    ggplot(aes(Accreditation, n, fill = Accreditation)) +
    geom_col() +
    facet_wrap(vars(Subject_Matter), scales = "free")

```

```{r}
top_gov <- museums %>% count(Governance) %>% slice_max(n, n = 4) %>% pull(Governance)

museums %>%
  filter(Governance %in% top_gov) %>%
  count(Governance, Accreditation) %>%
  ggplot(aes(Accreditation, n, fill = Accreditation)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(vars(Governance), scales = "free_y") +
  labs(x = NULL, y = "Number of museums")
```

```{r}
museum_parsed <-
  museums %>%
  select(museum_id, Accreditation, Governance, Size,
         Subject_Matter, Year_opened, Year_closed, Area_Deprivation_index) %>%
  mutate(Year_opened = parse_number(Year_opened),
         IsClosed = if_else(Year_closed == "9999:9999", "Open", "Closed")) %>%
  select(-Year_closed) %>%
  na.omit() %>%
  mutate(across(where(is.character), as.factor)) %>%
  mutate(museum_id = as.character(museum_id))

glimpse(museum_parsed)
```

## Feature engineering for high cardinality 

## *Split data
```{r}
library(tidymodels)

set.seed(123)
museum_split <- initial_split(museum_parsed, strata = Accreditation)

museum_train <- training(museum_split)
museum_test <- testing(museum_split)

set.seed(234)
museum_folds <- vfold_cv(museum_train, strata = Accreditation)
museum_folds
```

## *feature engineering
```{r}
library(embed)

museum_rec <- 
  recipe(Accreditation ~ ., data = museum_train) %>%
  update_role(museum_id, new_role = "id") %>%
  step_lencode_glm(Subject_Matter, outcome = vars(Accreditation)) %>%
  step_dummy(all_nominal_predictors())

museum_rec
```


```{r}
prep(museum_rec) %>% tidy(number = 1)
```

## *Model specification
```{r}
xgb_spec <- 
    boost_tree(
        mtry = tune(), 
        trees = tune(), 
        min_n = tune(), 
        learn_rate = 0.01
    ) %>%
    set_engine("xgboost") %>%
    set_mode("classification")

xgb_wf <- workflow(museum_rec, xgb_spec)
```


## *Tuning
```{r}
library(finetune)
doParallel::registerDoParallel()

set.seed(234)
xgb_rs <- 
    tune_grid(
        xgb_wf,
        museum_folds,
        control = control_grid(save_pred = TRUE)
    )

```

## *Show performance
```{r}
collect_metrics(xgb_rs)
collect_predictions(xgb_rs) %>%
    group_by(id) %>%
    roc_curve(Accreditation, .pred_Accredited) %>%
    autoplot()
```

## *Last fit
```{r}
xgb_last <- xgb_wf %>%
    tune::finalize_workflow(select_best(xgb_rs, "accuracy")) %>%
    last_fit(split = museum_split)

xgb_last
```

## *Show performance
```{r}
collect_metrics(xgb_last)
collect_predictions(xgb_last) %>%
    yardstick::conf_mat(Accreditation, .pred_class)
```

## *Variable importance
```{r}
library(vip)
xgb_last %>%
  extract_fit_engine() %>%
  vip()
```

