---
title: "Code Along 1"
subtitle: "Predicting IKEA Prices"
author: "Daniel Lee"
date: "2023-03-07"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

Our modeling goal is to predict the price of IKEA furniture from other furniture characteristics like category and size. 

We will use the latest tidyAML package.


## Explore Data

```{r}
library(tidyverse)
ikea <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv")

```

```{r}
ikea %>%
  select(...1, price, depth:width) %>%
  pivot_longer(depth:width, names_to = "dim") %>%
  ggplot(aes(value, price, color = dim)) +
  geom_point(alpha = 0.4, show.legend = FALSE) +
  scale_y_log10() +
  facet_wrap(~dim, scales = "free_x") +
  labs(x = NULL)
```

Transform data
log-transform and convert to factors
```{r}
ikea_df <- ikea %>%
  select(price, name, category, depth, height, width) %>%
  mutate(price = log10(price)) %>%
  mutate_if(is.character, factor)

ikea_df
```

## Build a Model

split data
```{r eval = FALSE}
library(tidymodels)

set.seed(123)
ikea_split <- initial_split(ikea_df, strata = price)
ikea_train <- training(ikea_split)
ikea_test  <- testing(ikea_split)

# Data are too small for cv
# rsample::vfold_cv(ikea_train)
set.seed(234)
ikea_folds <- rsample::bootstraps(ikea_train)
ikea_folds

```

```{r eval=FALSE}
library(usemodels)

usemodels::use_ranger(price ~ ., data = ikea_train)
```

```{r eval = FALSE}
library(textrecipes)
ranger_recipe <- 
  recipe(formula = price ~ ., data = ikea_train) %>%
    step_other(name, category, threshold = 0.01) %>%
    step_clean_levels(name, category) %>%
    step_impute_knn(depth, height, width)

ranger_spec <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_mode("regression") %>% 
  set_engine("ranger") 

ranger_workflow <- 
  workflow() %>% 
  add_recipe(ranger_recipe) %>% 
  add_model(ranger_spec) 

set.seed(57439)
ranger_tune <-
  tune_grid(ranger_workflow, 
            ikea_folds, 
            grid = 2)
```

Use tidyAML
I tried it 5/1/2023 and had trouble installing dependent packages.
Many dependent packages require the latest version of R and themselves.
Try it again in a few months.
```{r eval = FALSE}
library(textrecipes)
rec_obj <- 
  recipe(formula = price ~ ., data = ikea_df) %>%
    step_other(name, category, threshold = 0.01) %>%
    step_clean_levels(name, category) %>%
    step_impute_knn(depth, height, width)

library(tidyAML)
core_packages()

frt_tbl <- tidyAML::fast_regression(
    .data = ikea_df, 
    .rec_obj = rec_obj
    )
```



## Evaluate Models

1. View the best model
```{r}
show_best(ranger_tune, metric = "rmse")
autoplot(ranger_tune)
```

2. Fit the best model to train data
```{r}
final_ranger <- ranger_workflow %>%
    finalize_workflow(select_best(ranger_tune, metric = "rmse"))
```

3. Fit the best model to train data and evaluate on test data
```{r}
ikea_fit <- tune::last_fit(final_ranger, ikea_split)
```

4. Collect metrics
```{r}
tune::collect_metrics(ikea_fit)
```

5. Collect predictions
```{r}
tune::collect_predictions(ikea_fit)

collect_predictions(ikea_fit) %>%
    
    ggplot(aes(price, .pred)) +
    geom_point(alpha = 0.5, color = "midnightblue") +
    geom_abline(lty = 2, color = "gray50") +
    coord_fixed()
```

6. Predict
```{r}
ikea_fit %>%
    extract_workflow() %>%
    predict(ikea_test[1,])
```

7. View important variables

```{r}
library(vip)

imp_spec <- ranger_spec %>%
    tune::finalize_model(tune::select_best(ranger_tune)) %>%
    parsnip::set_engine("ranger", importance = "permutation")

workflows::workflow() %>%
    add_recipe(ranger_recipe) %>%
    add_model(imp_spec) %>%
    fit(ikea_train) %>%
    workflows::pull_workflow_fit() %>%
    vip()
```













### Question and Data

#### What is the research question?


#### Describe the data briefly.


#### Describe the first observation (the first row) in the data.




### Data Exploration and Transformation

#### What are the characteristics of the key variables used in the analysis? For example, which of the predictors seems to have correlations with the outcome variable? Does any variable have a skewed distribution, missing values, or incorrect information?


#### Describe the differences between the original data and the data transformed for modeling. Why?




### Data Preparation and Modeling

#### What are the names of data preparation steps (e.g., step_dummy) mentioned in the video?


#### What is the name of the machine learning models (e.g., random forest) used in the analysis?


#### Describe the steps taken for data preparation. Why?


#### Describe the characteristics of the models used in the analysis, including their advantages and disadvantages.




### Model Evaluation

#### What metrics are used in the model evaluation?


#### Describe the characteristics of the metrics used in the analysis, including their advantages and disadvantages.




### Conclusion

#### What are the major findings?
