---
title: "Apply it to your Data 9"
author: "Dean Stone"
date: "2023-04-20"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Explore Data

```{r}
library(tidyverse)
library(tidyquant)

big_tech_stock_prices <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_stock_prices.csv')
big_tech_companies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_companies.csv')
```

Explore data
```{r}
big_tech_stock_prices %>% count(stock_symbol) # META and TSLA have smaller number of rows

big_tech_stock_prices %>%
    group_by(stock_symbol) %>%
    slice_max(desc(date), n = 1)              # META starts in 2012-05-18 and TSLA in 2010-06-30

big_tech_stock_prices %>%
    group_by(stock_symbol) %>%
    slice_min(desc(date), n = 1)              # META ends in 2023-01-24

# Rearrange so all stocks have the same dates
big_tech_stock_prices <- big_tech_stock_prices %>%
    # Filter out so all stocks start in 2012-05-18
    filter(date >= "2012-05-018", date <= "2022-12-29")
```




```{r}
# standardize and normalize
stocks_tidy <- big_tech_stock_prices %>%
    
    group_by(stock_symbol) %>%
    
    tq_transmute(select     = adj_close, 
                 mutate_fun = periodReturn, 
                 period     = "monthly",
                 type       = "log") %>%
    
    ungroup()

stocks_tidy
```

```{r}
# Spread to the format required for clustering
stocks_demo <- stocks_tidy %>%
    pivot_wider(names_from = date, values_from = monthly.returns)

stocks_demo
```

## Implement k-means clustering

```{r}
stocks_clust <- kmeans(stocks_demo %>% select(-stock_symbol), centers = 3)
summary(stocks_clust)
```

```{r}
library(broom)
tidy(stocks_clust)
```

```{r}
augment(stocks_clust, stocks_demo) %>%
  ggplot(aes(`2022-12-29`, `2012-05-31`, color = .cluster)) +
  geom_point()
```

## Choosing K

```{r}
kclusts <-
  tibble(k = 1:9) %>%
  mutate(
    kclust = map(k, ~ kmeans(select(stocks_demo, -stock_symbol), .x)),
    glanced = map(kclust, glance)
  )

kclusts %>%
  unnest(cols = c(glanced)) %>%
  ggplot(aes(k, tot.withinss)) +
  geom_line(alpha = 0.5, size = 1.2, color = "midnightblue") +
  geom_point(size = 2, color = "midnightblue")
```

```{r}
final_clust <- kmeans(select(stocks_demo, -stock_symbol), centers = 5)
```

```{r}
library(plotly)

p <- augment(final_clust, stocks_demo) %>%
  ggplot(aes(`2022-12-29`, `2012-05-31`, color = .cluster, name = stock_symbol)) +
  geom_point()

ggplotly(p, height = 500)
```

```{r eval=F}
# Use UMAP to get 2-D Projection ----
# UMAP wouldn't work because the data is too small. A solution is to add more stocks.
library(umap)
?umap

umap_obj <- stocks_demo %>% 
    select(-stock_symbol) %>%
    umap()

umap_results_tbl <- umap_obj$layout %>%
    as_tibble() %>%
    set_names(c("x", "y")) %>%
    bind_cols(
        customer_product_tbl %>% select(bikeshop_name)
    )

umap_results_tbl %>%
    ggplot(aes(x, y)) +
    geom_point() + 
    geom_label_repel(aes(label = bikeshop_name), size = 3)
```


### Question and Data

#### What is the research question?


#### Describe the data briefly.


#### Which of the variables is the target variable (one that the model is predicting)? How is it different from the target variables from the first four case studies?


#### Describe the first observation (the first row) in the data.

### Data Exploration and Transformation

#### What are the characteristics of the key variables used in the analysis? For example, which of the predictors seems to have correlations with the outcome variable? Does any variable have a skewed distribution, missing values, or incorrect information?


#### Describe the differences between the original data and the data transformed for modeling. Why?



### Data Preparation and Modeling

#### What are the names of data preparation steps (e.g., step_dummy) mentioned in the video?


#### What is the name of the machine learning models (e.g., random forest) used in the analysis?


#### Describe the steps taken for data preparation. Why?


#### Describe the characteristics of the models used in the analysis, including their advantages and disadvantages.



### Model Evaluation

#### What metrics are used in the model evaluation?


#### Describe the characteristics of the metrics used in the analysis, including their advantages and disadvantages.



### Conclusion

#### What are the major findings?
