---
title: "Apply 11"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# for Core packages
library(tidyverse)

# for financial analysis
library(tidyquant)

# for times series
library(timetk)
```

Goal: Apply Matt Dancho's tutorial to state unemployment initial claims of New England states.

The following is the replication of [Matt Dancho's tutorial on this page](https://business-science.github.io/timetk/articles/TK05_Plotting_Seasonality_and_Correlation.html#stl-diagnostics)

```{r}
start_date <- "1989-01-01"

symbols_txt <- c("CTICLAIMS", # Connecticut
                 "MEICLAIMS", # Maine
                 "MAICLAIMS", # Massachusetts
                 "NHICLAIMS", # New Hampshire
                 "RIICLAIMS", # Rhode Island
                 "VTICLAIMS") # Vermont

claims_tbl <- tq_get(symbols_txt, get = "economic.data", from = start_date) %>%
    mutate(symbol = fct_recode(symbol,
                               "Connecticut"   = "CTICLAIMS",
                               "Maine"         = "MEICLAIMS",
                               "Massachusetts" = "MAICLAIMS",
                               "New Hampshire" = "NHICLAIMS",
                               "Rhode Island"  = "RIICLAIMS",
                               "Vermont"       = "VTICLAIMS")) %>%
    rename(claims = price)
```


## Plotting time series



### Box plots


### Regression plots



## Plotting Seasonality and Correlation

### Correlation Plots



### Seasonality



### STL Diagnostics



## Time Series Data Wrangling

### Summarize by Time



### Filter By Time



### Padding Data



### Sliding (Rolling) Calculations


