---
title: "Code Along 11"
author: "Daniel Lee"
date: "2023-05-01"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
library(timetk)
library(tidyquant)
```


## Plotting time series

```{r}
taylor_30_min

taylor_30_min %>%
    plot_time_series(.date_var = date, .value = value)
```

```{r}
m4_daily %>% count(id)

m4_daily %>%
    group_by(id) %>%
    plot_time_series(
        .date_var     = date, 
        .value        = value, 
        .facet_ncol   = 2, 
        .facet_scales = "free", 
        .interactive  = FALSE)
```

Visualizing Transformations & Sub-Groups

```{r}
m4_hourly %>% count(id)

m4_hourly %>%
    group_by(id) %>%
    plot_time_series(
        .date_var = date, 
        .value    = log(value), 
        .facet_ncol   = 2, 
        .facet_scales = "free", 
        .color_var = week(date))
```

Static ggplot2 Visualizations & Customizations

```{r}
taylor_30_min %>%
  plot_time_series(date, value, 
                   .color_var = month(date, label = TRUE),
                   
                   # Returns static ggplot
                   .interactive = FALSE, 
                   
                   # Customize
                   .title = "Taylor's MegaWatt Data", 
                   .x_lab = "Date (30-min intervals)", 
                   .y_lab = "Energy Demand (MW)", 
                   .color_lab = "Month")
```


### Box plots

```{r}
m4_monthly %>% count(id)

m4_monthly %>%
    filter_by_time(.date_var = date, .end_date = "1976") %>%
    group_by(id) %>%
    plot_time_series_boxplot(
        .date_var = date, 
        .value    = value, 
        .period   = "1 year", 
        .facet_ncol = 2)
```

### Regression plots

```{r}
m4_monthly %>%
    group_by(id) %>%
    plot_time_series_regression(
        .date_var = date, 
        .facet_ncol = 2, 
        .formula  = log(value) ~ as.numeric(date) + month(date, label = TRUE), 
        .show_summary = FALSE)
```

## Plotting Seasonality and Correlation

### Correlation Plots

```{r}
m4_hourly %>%
    group_by(id) %>%
    plot_acf_diagnostics(
        date, value, 
        .lags = "7 days")
```

```{r}
walmart_sales_weekly %>%
    group_by(id) %>%
    plot_acf_diagnostics(
        Date, Weekly_Sales, 
        .ccf_vars = c(Temperature, Fuel_Price), 
        .lags = "3 months")
```


### Seasonality

```{r}
taylor_30_min %>%
    plot_seasonal_diagnostics(date, value)
```

```{r}
m4_hourly %>% count(id)

m4_hourly %>%
    group_by(id) %>%
    plot_seasonal_diagnostics(date, value)
```

### STL Diagnostics

```{r}
m4_hourly %>%
    group_by(id) %>%
    plot_stl_diagnostics(
        date, value,
        .feature_set = c("observed", "season", "trend", "remainder"))
```

## Time Series Data Wrangling

### Summarize by Time
daily data
```{r}
FANG %>%
  group_by(symbol) %>%
  plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE)
```

summarize it by quarter
```{r}
FANG %>%
    group_by(symbol) %>%
    summarise_by_time(.date_var = date, volume = sum(volume), .by = "quarter") %>%
    plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE)
```

```{r}
FANG %>%
    group_by(symbol) %>%
    summarise_by_time(.date_var = date, adjusted = mean(adjusted), .by = "month") %>%
    plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)
```


### Filter By Time

```{r}
FANG %>%
    group_by(symbol) %>%
    filter_by_time(.date_var = date, 
                   .start_date = "2013-09", 
                   .end_date = "2013") %>%
    plot_time_series(date, adjusted, .facet_ncol = 2)
```

### Padding Data

```{r}
FANG %>%
    group_by(symbol) %>%
    pad_by_time(date, .by = "day", .pad_value = 0)
```

### Sliding (Rolling) Calculations

```{r}
FANG %>%
    head(10) %>%
    mutate(rolling_avg_2 = slidify_vec(adjusted, mean, 
                                       .period = 2, 
                                       .align = "right", 
                                       .partial = TRUE))
```


```{r}
# Rolling regressions are easy to implement using `.unlist = FALSE`
lm_roll <- slidify(~ lm(..1 ~ ..2 + ..3), .period = 90, 
                   .unlist = FALSE, .align = "right")


FANG %>%
  select(symbol, date, adjusted, volume) %>%
  group_by(symbol) %>%
  mutate(numeric_date = as.numeric(date)) %>%
  # Apply rolling regression
  mutate(rolling_lm = lm_roll(adjusted, volume, numeric_date)) %>%
  filter(!is.na(rolling_lm))
```

