---
title: "Time Series Data Wrangling"
author: "Daniel Lee"
date: "2023-04-17"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidyquant)
library(timetk)
```

Goal: Apply Matt Dancho's tutorial to state unemployment initial claims of New England states.

The following is the replication of [Matt Dancho's tutorial on this page](https://business-science.github.io/timetk/articles/TK07_Time_Series_Data_Wrangling.html)

```{r}
symbols_txt <- c("CTICLAIMS", # Connecticut
                 "MEICLAIMS", # Maine
                 "MAICLAIMS", # Massachusetts
                 "NHICLAIMS", # New Hampshire
                 "RIICLAIMS", # Rhode Island
                 "VTICLAIMS") # Vermont

claims_tbl <- tq_get(symbols_txt, get = "economic.data") %>%
    mutate(symbol = fct_recode(symbol,
                               "Connecticut"   = "CTICLAIMS",
                               "Maine"         = "MEICLAIMS",
                               "Massachusetts" = "MAICLAIMS",
                               "New Hampshire" = "NHICLAIMS",
                               "Rhode Island"  = "RIICLAIMS",
                               "Vermont"       = "VTICLAIMS")) %>%
    rename(claims = price)
```

## Visualize timeseries
```{r}
claims_tbl %>%
    group_by(symbol) %>%
    timetk::plot_time_series(.date_var = date, .value = claims, .facet_ncol = 2)

claims_tbl %>%
    group_by(symbol) %>%
    timetk::plot_time_series(.date_var = date, .value = claims, .facet_ncol = 2, .interactive = FALSE) + coord_cartesian(ylim = c(0,1e4))
```

## Summarize by Time

```{r}
claims_tbl %>%
    group_by(symbol) %>%
    timetk::summarise_by_time(.date_var = date,
                              .by       = "month", 
                              claims    = sum(claims)) %>%
    timetk::plot_time_series(date, claims, .facet_ncol = 2)
```

## Filter by Time 
```{r}
claims_tbl %>%
    timetk::filter_by_time(.date_var = date, .start_date = "start", .end_date = "2020-02") 

claims_tbl %>%
    timetk::filter_by_time(.date_var = date, .start_date = "start", .end_date = "2020-02") %>%
    group_by(symbol) %>% slice((n()-1):n())
```

## Padding data

### Fill in gaps
```{r}
claims_tbl %>%
    group_by(symbol) %>%
    slice_max(order_by = desc(date), n = 2) %>%
    timetk::pad_by_time(.date_var = date, .by = "day", .fill_na_direction = "down")
```

### Low to high frequency
```{r}
claims_tbl %>%
    group_by(symbol) %>%
    # slice_max(order_by = desc(date), n = 2) %>%
    timetk::pad_by_time(.date_var = date, .by = "day") %>%
    mutate(claims_interp = ts_impute_vec(claims, period =1)) %>%
    filter_by_time(.date_var = date, "start", first(date) %+time% "1 month") %>%
    plot_time_series(.date_var = date, 
                     .value = claims_interp, 
                     .facet_ncol = 2, 
                     .smooth = FALSE)
```

## Sliding (Rolling) Calculations

### Rolling mean
```{r}
FANG %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  # Apply roll apply Function
  mutate(rolling_avg_30 = slidify_vec(adjusted,  mean, 
                                      .period = 30, .partial = TRUE))
```

### Rolling regression
Objective: Calculate a rolling regression.

* This is a complex sliding (rolling) calculation that requires multiple columns to be involved.
* slidify() is built for this.
* Use the multi-variable purrr ..1, ..2, ..3, etc notation to setup a function

```{r}
# Rolling regressions are easy to implement using `.unlist = FALSE`
lm_roll <- slidify(~ lm(..1 ~ ..2 + ..3), .period = 90, 
                   .unlist = FALSE, .align = "right")


FANG %>%
  select(symbol, date, adjusted, volume) %>%
  group_by(symbol) %>%
  mutate(numeric_date = as.numeric(date)) %>%
  # Apply rolling regression
  mutate(rolling_lm = lm_roll(adjusted, volume, numeric_date)) %>%
  filter(!is.na(rolling_lm))
```

```{r}
# Rolling regressions are easy to implement using `.unlist = FALSE`
lm_roll <- slidify(~ lm(..1 ~ ..2), .period = 90, 
                   .unlist = FALSE, .align = "right")


claims_tbl %>%
  group_by(symbol) %>%
  mutate(numeric_date = as.numeric(date)) %>%
  # Apply rolling regression
  mutate(rolling_lm = lm_roll(claims, numeric_date)) %>%
  filter(!is.na(rolling_lm))
```





