---
title: "Time Series Data Wrangling"
author: "Daniel Lee"
date: "2023-04-17"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

library(tidyverse)
library(tidyquant)
library(timetk)
```

Goal: Apply Matt Dancho's tutorial to state unemployment initial claims of New England states.

The following is the replication of [Matt Dancho's tutorial on this page](https://business-science.github.io/timetk/articles/TK05_Plotting_Seasonality_and_Correlation.html#stl-diagnostics)

```{r}
start_date <- "1989-01-01"

symbols_txt <- c("CTICLAIMS", # Connecticut
                 "MEICLAIMS", # Maine
                 "MAICLAIMS", # Massachusetts
                 "NHICLAIMS", # New Hampshire
                 "RIICLAIMS", # Rhode Island
                 "VTICLAIMS") # Vermont

claims_tbl <- tq_get(symbols_txt, get = "economic.data", from = start_date) %>%
    mutate(symbol = fct_recode(symbol,
                               "Connecticut"   = "CTICLAIMS",
                               "Maine"         = "MEICLAIMS",
                               "Massachusetts" = "MAICLAIMS",
                               "New Hampshire" = "NHICLAIMS",
                               "Rhode Island"  = "RIICLAIMS",
                               "Vermont"       = "VTICLAIMS")) %>%
    rename(claims = price)
```

## Correlation Plots

### ACF Diagnostics
Lags correlated with the original series: lag 1, lag 534, and lag 537
```{r}
claims_tbl %>%
    plot_acf_diagnostics(date, .value = claims, .lags = "1 month")
```

### Grouped ACF Diagnostics

```{r}
claims_tbl %>%
    group_by(symbol) %>%
    plot_acf_diagnostics(date, .value = claims, .lags = "1 month")
```

### Grouped CCF Plots

Check correlation with other series and their lags.
```{r}
claims_us_tbl <- tq_get(x = "ICNSA", get = "economic.data", from = start_date) %>%
    rename(claims_us = price) %>%
    select(-symbol)

ffr_daily_tbl <- tq_get(x = "DFF", get = "economic.data", from = start_date)
ffr_weekly_tbl <- ffr_daily_tbl %>%
    summarise_by_time(.date_var = date, .by = "week", ffr = mean(price, na.rm = TRUE)) %>%
    # Add 6 days to align with other series
    mutate(date = date %+time% "6 days")


claims_ne_us_ffr_tbl <- claims_tbl %>%
    left_join(claims_us_tbl) %>%
    left_join(ffr_weekly_tbl)

claims_ne_us_ffr_tbl %>%
    plot_acf_diagnostics(
        date, claims,                 # ACF & PACF
        .ccf_vars = c(claims_us, ffr), # Cross Correlation F
        .lags = "3 months")

claims_ne_us_ffr_tbl %>%
    plot_acf_diagnostics(
        date, claims,                 # ACF & PACF
        .ccf_vars = c(claims_us, ffr), # Cross Correlation F
        .lags = "3 months", 
        .show_ccf_vars_only = TRUE)


claims_ne_us_ffr_tbl %>%
    group_by(symbol) %>%
    plot_acf_diagnostics(
        date, claims,                 # ACF & PACF
        .ccf_vars = c(claims_us, ffr), # Cross Correlation F
        .lags = "1 month", 
        .show_ccf_vars_only = TRUE)
```

## Seasonality

### Seasonal Visualizations
```{r}
claims_tbl %>%
    plot_seasonal_diagnostics(date, claims)

claims_tbl %>%
    plot_seasonal_diagnostics(date, log(claims))
```

### Grouped Seasonal Visualizations
```{r}
claims_tbl %>%
    group_by(symbol) %>%
    plot_seasonal_diagnostics(date, log(claims))


claims_tbl %>%
    filter(symbol %in% c("New Hampshire", "Massachusetts")) %>%
    group_by(symbol) %>%
    plot_seasonal_diagnostics(date, log(claims))

# Remove impacts of the Pandemic
claims_tbl %>%
    filter(symbol %in% c("New Hampshire", "Massachusetts")) %>%
    filter_by_time(date, .end_date = "2020-02")%>%
    group_by(symbol) %>%
    plot_seasonal_diagnostics(date, log(claims))
```

## STL Diagnostics
```{r}
claims_tbl %>%
    group_by(symbol) %>%
    plot_stl_diagnostics(
        date, log(claims),
        .feature_set = c("observed", "season", "trend", "remainder"),
        .facet_scales = "free_y")

claims_tbl %>%
    filter(symbol %in% c("New Hampshire", "Massachusetts")) %>%
    group_by(symbol) %>%
    plot_stl_diagnostics(
        date, log(claims),
        .feature_set = c("observed", "season", "trend", "remainder"),
        .facet_scales = "free_y")
```

